---
title: "Data 607 Project Proposal"
author: "Jaya Veluri"
date: "11/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
## Project 
### Goal1: Analyze the correlation of twitter sentiment analysis on stock prices like Microsoft,Apple,Tesla.

Twitter is a large social platform where users are free to share whatever is on their mind in brief text messages. There are many users on twitter, most belonging to the general public, however, many companies have joined the platform to help keep up their public relations. In this project we will try to better understand the trends on twitter and assess if there is any relationship between twitter sentiment and stock price.

### Goal2 : Graph Database

We Collect the Data in Goal1 and port to a graph database such as MongoDB Atlas or Neo4j.


```{r}


```
## Data
To collect the data we use the twitteR package and requested data from the Twitter Search API (https://api.twitter.com/1.1/search/tweets.json). We narrowed our search to tweets that contained Microsoft,Tesla and Apple affiliated twitter handles.

```{r}

```



